Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-05 Paper/main.tex
Editing part of conclusion

Lastly, a comparison of the ExaWind solvers Nalu-Wind and AMR-Wind was
conducted using the stable offshore boundary layer at 5 m/s.  The mean
statistics were found to agree well between the two LES codes.  Small
differences were found in wind profiles at higher elevations and for
the peak $S_u$ spectra, and excellent matches were observed for the
averaged veer, temperature, and TI profiles.

>>>>

Lastly, a comparison of the ExaWind solvers Nalu-Wind and AMR-Wind was
conducted using the stable offshore boundary layer at 5 m/s.  The mean
statistics were found to agree well between the two LES codes.  Small
differences were found in wind profiles at higher elevations and for
the peak $S_u$ spectra, and excellent matches were observed for the
averaged veer, temperature, and TI profiles.  For the problem sizes
considered here, it was also found that AMR-Wind was significantly
more computationally efficient than Nalu-Wind when measured on a time
per degree of freedom basis.  However, the good agreement is a
promising indication that the two codes can be used together
effectively for future wind farm applications, where the highly
efficient, structured nature of AMR-Wind handles the free stream
boundary layer and is combined with the unstructured Nalu-Wind solver
for complex turbine geometries.

% The performance difference may be caused
% by XXX, but warrants further investigation in future work.
